Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Added structure for disc RQ2

\subsubsection{Conservation of Organisational Stability}
The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0. As mentioned in Section \ref{law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions. Consequently, the only significant update to the API was made in the transition to version 2.0. The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed. This suggests that the law of conservation of organisational stability does not apply to APIs.

@@

\subsubsection{Declining Quality}
The interviews established that a groomative motive was not the most major reason for implementing any change. The changes to the example code and the SDK, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content. These changes did, however, increase the quality and was a substantial part of the changes, which could have been left out. A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{law2}. We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.

\subsubsection{Feedback System}
One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop. Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users in this loop. The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed. One example of how the API users have been included in the feedback loop, was prior to version 2.0 being released, when API users implemented functionality related to sound, even though there was no interface for this in the API. The experiences of this API user, were later considered when developing the axsound module. One benefit of having a more structured feedback loop, would be that the API developers would be more and faster aware of potential errors in the implementation of the API. Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API. This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects. Because of these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.

@@

\subsection{RQ2}
You can't assume

>>>>

\subsubsection{Conservation of Organisational Stability}
The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0. As mentioned in Section \ref{sec:law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions. Consequently, the only significant update to the API was made in the transition to version 2.0. The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed. This suggests that the law of conservation of organisational stability does not apply to APIs.

@@

\subsubsection{Declining Quality}
The interviews established that a groomative motive was not the most major reason for implementing any change. The changes to the example code and the SDK, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content. These changes did, however, increase the quality and was a substantial part of the changes, which could have been left out. A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}. We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.

\subsubsection{Feedback System}
One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop. Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users in this loop. The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed. One example of how the API users have been included in the feedback loop, was prior to version 2.0 being released, when API users implemented functionality related to sound, even though there was no interface for this in the API. The experiences of this API user, were later considered when developing the axsound module. One benefit of having a more structured feedback loop, would be that the API developers would be more and faster (!!!re-phrase) aware of potential errors in the implementation of the API. Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API. This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects. Because of these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.

@@

\subsection{RQ2}
1.
Feedback system: 
Something that is very important and might be overlooked in API development/evolution

2. 
Why don't all theories apply? 
Try explain what the reason might be, by comparing APIs to normal systems. 
(Complexity and quality) These apply, but it seems that they are not very important compared to for exmaple functionality. Maybe they are true to a lesser extent compared to normal systems. 
This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases.

3.
The true ones 
List the ones that we found a lot of evidence  (the most true: 6,7) (1, 3, 5) and explain why they are true by linking it to RQ1 results
